Guarded Recursion in Agda via Sized Types

### 2019-01-15 code-oneclock-paper/latex/Introduction.tex
Work on introduction

The relation between those approaches...

To compare these two approaches, we develop denotational semantics of guarded recursive type theory in a type theory with sized types.
More specifically, we define a presheaf model of a simple type theory with guarded recursion \cite{BMSS-synthetic}.
Simple types are interpreted via the usual presheaf semantics.

@@

Our contributions are as follows
\begin{enumerate}
	\item We give a new model of guarded recursive type theory;
	\item We give a formal relation between sized types and guarded recursion;
	\item The construction is formalized.
\end{enumerate}

In Section 2, we describe the meta-theory in which we work.
In Section 3, we describe the object theory.
This is basically a variant of guarded recursion as done by Atkey and McBride \cite{atkey2013productive}.
In Section 4, we define the model and give the interpretation of simple type operators.
In Section 5, we interpret guarded recursion and guarded recursive types.
Finally, we give an overview of the interpretation in Section 6.

>>>>

To compare the strength of these two approaches, we develop denotational semantics of guarded recursive type theory in a type theory with sized types.
This shows that guarded recursive type theory can be done via sized types.
More specifically, we define a presheaf model of a simple type theory with guarded recursion \cite{BMSS-synthetic}.
Simple types are interpreted via the usual presheaf semantics.

@@

Our contributions are as follows
\begin{enumerate}
	\item We give a new denotational semantics of guarded recursive type theory in type theory;
	\item We show that guarded recursion can be interpreted in sized types.
	\item We formally prove the syntax is consistent.
\end{enumerate}

In Section 2, we describe the meta-theory in which we work.
In Section 3, we describe the syntax of the object theory, which is basically a variant of guarded recursion as done by Atkey and McBride \cite{atkey2013productive}.
We do this in the form of a deep embedding.
More specifically, we define data types representing the contexts, types, terms, and so on, and we give the rules for definitional equality.
In Sections 4 and 5, we define the denotational semantics of this syntax.
First, we give the interpretation of context, types, and terms in the model, and we show how to interpret simple type formers.
Then we show this model supports guarded recursion and guarded recursive types.
Finally, we show the syntax is consistent in Section 6.
